TSELM: Target speaker extraction using discrete tokens and language models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-06 src/paper.tex
update

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{bm}
\usepackage{multirow}
\usepackage{tabularx, colortbl, makecell}
\usepackage{etoolbox}

@@

\title{Target Speaker Extraction using Discrete Representations from 
Self-Supervised Models and Language Models
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Beilong Tang}
\IEEEauthorblockA{\textit{Duke Kunshan University} \\
% \textit{name of organization (of Aff.)}\\
Kunshan, China \\
bt132@duke.edu}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Bang Zeng}
\IEEEauthorblockA{\textit{Duke Kunshan University} \\
% \textit{name of organization (of Aff.)}\\
Kunshan, China \\
bangzeng@whu.edu.cn}
% \and
% \IEEEauthorblockN{3\textsuperscript{rd} Zhan Jin}
% \IEEEauthorblockA{\textit{Duke Kunshan University} \\
% Kunshan, China \\
% zhan.jin@whu.edu.cn}
\and
\IEEEauthorblockN{3\textsuperscript{re} Ming Li}
\IEEEauthorblockA{\textit{Duke Kunshan University} \\
% \textit{name of organization (of Aff.)}\\
Kunshan, China \\
ming.li369@dukekunshan.edu.cn}
}

@@

Finally, we have observed a performance gap between discrete methods and continuous methods.

>>>>

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{bm}
\usepackage{multirow}
\usepackage{tabularx, colortbl, makecell}
\usepackage{etoolbox}
\usepackage{hyperref}

@@

\title{TSELM: Target speaker extraction using discrete tokens and language models
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Beilong Tang}
\IEEEauthorblockA{\textit{Duke Kunshan University} \\
% \textit{name of organization (of Aff.)}\\
Kunshan, China \\
bt132@duke.edu}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Bang Zeng}
\IEEEauthorblockA{\textit{Duke Kunshan University} \\
% \textit{name of organization (of Aff.)}\\
Kunshan, China \\
bangzeng@whu.edu.cn}
% \and
% \IEEEauthorblockN{3\textsuperscript{rd} Zhan Jin}
% \IEEEauthorblockA{\textit{Duke Kunshan University} \\
% Kunshan, China \\
% zhan.jin@whu.edu.cn}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Ming Li}
\IEEEauthorblockA{\textit{Duke Kunshan University} \\
% \textit{name of organization (of Aff.)}\\
Kunshan, China \\
ming.li369@dukekunshan.edu.cn}
}

@@

Finally, we have observed a performance gap between discrete methods and continuous methods (Continuous-WavLM-L6) on target 
speaker extraction as shown in Table \ref{main_exp}. For Continuous-WavLM-L6,
we use the 6th layer embedding output from WavLM from both the mixed speech and reference speech, and use MSE loss between the output from LM and the clean embeddings. This method 
has the best performance in terms of DNSMOS and dWER. It has a better dWER of 13.6\% compared with TSELM-L. This might be related to the 
information loss of discretization process. We hope future research will work to bridge the gap.
